visitation_bias

### 2021-06-11 code/ms2_nullmodels.Rmd
working on discussion

check.gamViz(gam3.1)
gam3.1_sum <- summary(gam3.1, re.test = FALSE)
plot.gamViz(gam3.1, allTerms = TRUE)

gam3.1b <- bam(preference ~
                bb.ktype +
                s(site, by = bb.ktype, bs = "re") +
                s(year, by = bb.ktype, bs = "re") +
                te(yday, elev.mean, by = bb.ktype),
              family = "gaussian",
              method = "fREML",
              discrete = TRUE,
              data = filter(null_tab3_join, 
                            bb.sp %in% c("hort", "prat", "telu", 
                                         "wurf", "soro", "pasc") &
                              ktype %in% c("bell", "lip", "flag", "head") &
                              prop.cover < 0.5)) %>% 
                getViz()

check.gamViz(gam3.1b)
gam3.1b_sum <- summary(gam3.1b, re.test = FALSE)
plot.gamViz(gam3.1b, allTerms = TRUE)
```

@@

ggsave("../ms_2/figures/preference_lability_gam.pdf", height = 5, width = 6.5)
ggsave("../ms_2/figures/preference_lability_gam.png", height = 5, width = 6.5)

# And now having dropped the high abundance outliers
gam3.1b_s_table <- gam3.1b_sum$s.table %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  filter(str_detect(term, "te\\(")) %>%
  mutate(term = str_extract(term, ".{6}$")) %>%
  separate(term, c("bb.sp", "ktype")) %>%
  mutate(ktype = case_when(
    ktype == 3 ~ "bell",
    ktype == 5 ~ "lip",
    ktype == 6 ~ "flag",
    ktype == 7 ~ "head"
  )) %>%
  mutate(pval = signif(`p-value`, digits = 3)) %>%
  select(bb.sp, ktype, edf, pval) %>%
  as_tibble() %>%
  mutate(ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")))

# Extract plotting data.
hort_3_gam3.1b <- plot(sm(gam3.1b, 49))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("bell", n()))

hort_5_gam3.1b <- plot(sm(gam3.1b, 50))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("lip", n()))

hort_6_gam3.1b <- plot(sm(gam3.1b, 51))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("flag", n()))

hort_7_gam3.1b <- plot(sm(gam3.1b, 52))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("head", n()))

pasc_3_gam3.1b <- plot(sm(gam3.1b, 53))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("bell", n()))

pasc_5_gam3.1b <- plot(sm(gam3.1b, 54))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("lip", n()))

pasc_6_gam3.1b <- plot(sm(gam3.1b, 55))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("flag", n()))

pasc_7_gam3.1b <- plot(sm(gam3.1b, 56))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("head", n()))

prat_3_gam3.1b <- plot(sm(gam3.1b, 57))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("bell", n()))

prat_5_gam3.1b <- plot(sm(gam3.1b, 58))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("lip", n()))

prat_6_gam3.1b <- plot(sm(gam3.1b, 59))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("flag", n()))

prat_7_gam3.1b <- plot(sm(gam3.1b, 60))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("head", n()))

soro_3_gam3.1b <- plot(sm(gam3.1b, 61))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("bell", n()))

soro_5_gam3.1b <- plot(sm(gam3.1b, 62))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("lip", n()))

soro_6_gam3.1b <- plot(sm(gam3.1b, 63))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("flag", n()))

soro_7_gam3.1b <- plot(sm(gam3.1b, 64))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("head", n()))

telu_3_gam3.1b <- plot(sm(gam3.1b, 65))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("bell", n()))

telu_5_gam3.1b <- plot(sm(gam3.1b, 66))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("lip", n()))

telu_6_gam3.1b <- plot(sm(gam3.1b, 67))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("flag", n()))

telu_7_gam3.1b <- plot(sm(gam3.1b, 68))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("head", n()))

wurf_3_gam3.1b <- plot(sm(gam3.1b, 69))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("bell", n()))

wurf_5_gam3.1b <- plot(sm(gam3.1b, 70))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("lip", n()))

wurf_6_gam3.1b <- plot(sm(gam3.1b, 71))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("flag", n()))

wurf_7_gam3.1b <- plot(sm(gam3.1b, 72))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("head", n()))

plotting_data__gam3.1b <- bind_rows(hort_3_gam3.1b, hort_5_gam3.1b, hort_6_gam3.1b, hort_7_gam3.1b,
                           pasc_3_gam3.1b, pasc_5_gam3.1b, pasc_6_gam3.1b, pasc_7_gam3.1b,
                           prat_3_gam3.1b, prat_5_gam3.1b, prat_6_gam3.1b, prat_7_gam3.1b,
                           soro_3_gam3.1b, soro_5_gam3.1b, soro_6_gam3.1b, soro_7_gam3.1b,
                           telu_3_gam3.1b, telu_5_gam3.1b, telu_6_gam3.1b, telu_7_gam3.1b,
                           wurf_3_gam3.1b, wurf_5_gam3.1b, wurf_6_gam3.1b, wurf_7_gam3.1b) %>%
  group_by(bb.sp, ktype) %>%
  mutate(z.norm = scale(z, center = FALSE),
         ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")),
         date = as_date(x)) %>%
  ungroup() %>%
  left_join(bb_traits) %>%
  left_join(gam3.1b_s_table) %>%
  select(z, z.norm, date, x, elevation = y, se, 
         bb.sp, ktype, pbl.w, edf, pval) %>%
  mutate(sig = if_else(pval < 0.05, TRUE, FALSE))

ggplot(plotting_data__gam3.1b, aes(date, elevation, z = z.norm, fill = z.norm)) +
  geom_raster() +
  geom_contour(color = "black",
               size = 0.1,
               bins = 40,
               aes(linetype = sig)) + # by fixing bins, we scale contours to each plot while letting the color ramp represent differences in scale across plots; I think this is a good compromise
  facet_grid(reorder(bb.sp, -pbl.w) ~ ktype) +
  scale_linetype_manual(values = c("dotted", "solid"))+
  scale_fill_viridis_c(na.value = "transparent") +
  labs(x = NULL, y = "Elevation (m)", fill = "Normalized\neffect", linetype = "p < 0.05") +
  theme_light(12) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5))

@@

@@

### 4.3 A binomial model: significant preference 0/1
One way to get around this problem is to model bias as a binary response, either significantly positive or not. 
#### 4.3.1 Call model
```{r}
null_tab3_bin <- null_tab3 %>%
  mutate(preference.bin = as.integer(if_else(Test == "Stronger", 1, 0)))

gam3.2 <- bam(preference.bin ~
                bb.ktype +
                s(site, by = bb.ktype, bs = "re") +
                s(year, by = bb.ktype, bs = "re") +
                te(yday, elev.mean, by = bb.ktype),
              family = "binomial",
              method = "fREML",
              discrete = TRUE,
              data = filter(null_tab3_bin, 
                            bb.sp %in% c("hort", "prat", "telu", 
                                         "wurf", "soro", "pasc") &
                              ktype %in% c("bell", "lip", "flag", "head"))) %>% 
                getViz()

check.gamViz(gam3.2)
gam3.2_sum <- summary(gam3.2, re.test = FALSE)
print(plot.gamViz(gam3.2, allTerms = TRUE), pages = 4)
```

#### 4.3.2 Plot model
```{r}
# Tabulate model summary
gam3.2_s_table <- gam3.2_sum$s.table %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  filter(str_detect(term, "te\\(")) %>%
  mutate(term = str_extract(term, ".{6}$")) %>%
  separate(term, c("bb.sp", "ktype")) %>%
  mutate(ktype = case_when(
    ktype == 3 ~ "bell",
    ktype == 5 ~ "lip",
    ktype == 6 ~ "flag",
    ktype == 7 ~ "head"
  )) %>%
  mutate(pval = signif(`p-value`, digits = 3)) %>%
  select(bb.sp, ktype, edf, pval) %>%
  as_tibble() %>%
  mutate(ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")))

# Extract plotting data.
hort_3 <- plot(sm(gam3.2, 49))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("bell", n()))

hort_5 <- plot(sm(gam3.2, 50))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("lip", n()))

hort_6 <- plot(sm(gam3.2, 51))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("flag", n()))

hort_7 <- plot(sm(gam3.2, 52))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("head", n()))

pasc_3 <- plot(sm(gam3.2, 53))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("bell", n()))

pasc_5 <- plot(sm(gam3.2, 54))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("lip", n()))

pasc_6 <- plot(sm(gam3.2, 55))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("flag", n()))

pasc_7 <- plot(sm(gam3.2, 56))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("head", n()))

prat_3 <- plot(sm(gam3.2, 57))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("bell", n()))

prat_5 <- plot(sm(gam3.2, 58))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("lip", n()))

prat_6 <- plot(sm(gam3.2, 59))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("flag", n()))

prat_7 <- plot(sm(gam3.2, 60))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("head", n()))

soro_3 <- plot(sm(gam3.2, 61))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("bell", n()))

soro_5 <- plot(sm(gam3.2, 62))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("lip", n()))

soro_6 <- plot(sm(gam3.2, 63))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("flag", n()))

soro_7 <- plot(sm(gam3.2, 64))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("head", n()))

telu_3 <- plot(sm(gam3.2, 65))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("bell", n()))

telu_5 <- plot(sm(gam3.2, 66))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("lip", n()))

telu_6 <- plot(sm(gam3.2, 67))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("flag", n()))

telu_7 <- plot(sm(gam3.2, 68))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("head", n()))

wurf_3 <- plot(sm(gam3.2, 69))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("bell", n()))

wurf_5 <- plot(sm(gam3.2, 70))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("lip", n()))

wurf_6 <- plot(sm(gam3.2, 71))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("flag", n()))

wurf_7 <- plot(sm(gam3.2, 72))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("head", n()))

plotting_data <- bind_rows(hort_3, hort_5, hort_6, hort_7,
                           pasc_3, pasc_5, pasc_6, pasc_7,
                           prat_3, prat_5, prat_6, prat_7,
                           soro_3, soro_5, soro_6, soro_7,
                           telu_3, telu_5, telu_6, telu_7,
                           wurf_3, wurf_5, wurf_6, wurf_7) %>%
  group_by(bb.sp, ktype) %>%
  mutate(z.norm = scale(z, center = FALSE),
         ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")),
         date = as_date(x)) %>%
  ungroup() %>%
  left_join(bb_traits) %>%
  left_join(gam3.2_s_table) %>%
  select(z, z.norm, date, x, elevation = y, se, 
         bb.sp, ktype, pbl.w, edf, pval) %>%
  mutate(sig = if_else(pval < 0.05, TRUE, FALSE))

ggplot(plotting_data, aes(date, elevation, z = z.norm, fill = z.norm)) +
  geom_raster() +
  geom_contour(color = "black",
               size = 0.1,
               bins = 40,
               aes(linetype = sig)) + # by fixing bins, we scale contours to each plot while letting the color ramp represent differences in scale across plots; I think this is a good compromise
  facet_grid(reorder(bb.sp, -pbl.w) ~ ktype) +
  scale_linetype_manual(values = c("dotted", "solid"))+
  scale_fill_viridis_c(na.value = "transparent") +
  labs(x = NULL, y = "Elevation (m)", fill = "Normalized\neffect", linetype = "p < 0.05") +
  theme_light(12) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5))
```

### 4.4 A normalized model: proportion of maximum/minimum preference
#### 4.4.1 Call model
```{r}
gam3.3 <- bam(preference.norm ~
                bb.ktype +
                s(site, by = bb.ktype, bs = "re") +
                s(year, by = bb.ktype, bs = "re") +
                te(yday, elev.mean, by = bb.ktype),
              family = "gaussian",
              method = "fREML",
              discrete = TRUE,
              data = filter(null_tab3.norm, 
                            bb.sp %in% c("hort", "prat", "telu", 
                                         "wurf", "soro", "pasc") &
                              ktype %in% c("bell", "lip", "flag", "head"))) %>% 
                getViz()

check.gamViz(gam3.3)
gam3.3_sum <- summary(gam3.3, re.test = FALSE)
print(plot.gamViz(gam3.3, allTerms = TRUE), pages = 4)
```

#### 4.4.2 Plot model
```{r}
# Tabulate model summary
gam3.3_s_table <- gam3.3_sum$s.table %>%
  as.data.frame() %>%
  rownames_to_column("term") %>%
  filter(str_detect(term, "te\\(")) %>%
  mutate(term = str_extract(term, ".{6}$")) %>%
  separate(term, c("bb.sp", "ktype")) %>%
  mutate(ktype = case_when(
    ktype == 3 ~ "bell",
    ktype == 5 ~ "lip",
    ktype == 6 ~ "flag",
    ktype == 7 ~ "head"
  )) %>%
  mutate(pval = signif(`p-value`, digits = 3)) %>%
  select(bb.sp, ktype, edf, pval) %>%
  as_tibble() %>%
  mutate(ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")))

# Extract plotting data.
hort_3 <- plot(sm(gam3.3, 49))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("bell", n()))

hort_5 <- plot(sm(gam3.3, 50))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("lip", n()))

hort_6 <- plot(sm(gam3.3, 51))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("flag", n()))

hort_7 <- plot(sm(gam3.3, 52))$ggObj[[1]] %>%
  mutate(bb.sp = rep("hort", n()),
         ktype = rep("head", n()))

pasc_3 <- plot(sm(gam3.3, 53))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("bell", n()))

pasc_5 <- plot(sm(gam3.3, 54))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("lip", n()))

pasc_6 <- plot(sm(gam3.3, 55))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("flag", n()))

pasc_7 <- plot(sm(gam3.3, 56))$ggObj[[1]] %>%
  mutate(bb.sp = rep("pasc", n()),
         ktype = rep("head", n()))

prat_3 <- plot(sm(gam3.3, 57))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("bell", n()))

prat_5 <- plot(sm(gam3.3, 58))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("lip", n()))

prat_6 <- plot(sm(gam3.3, 59))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("flag", n()))

prat_7 <- plot(sm(gam3.3, 60))$ggObj[[1]] %>%
  mutate(bb.sp = rep("prat", n()),
         ktype = rep("head", n()))

soro_3 <- plot(sm(gam3.3, 61))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("bell", n()))

soro_5 <- plot(sm(gam3.3, 62))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("lip", n()))

soro_6 <- plot(sm(gam3.3, 63))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("flag", n()))

soro_7 <- plot(sm(gam3.3, 64))$ggObj[[1]] %>%
  mutate(bb.sp = rep("soro", n()),
         ktype = rep("head", n()))

telu_3 <- plot(sm(gam3.3, 65))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("bell", n()))

telu_5 <- plot(sm(gam3.3, 66))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("lip", n()))

telu_6 <- plot(sm(gam3.3, 67))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("flag", n()))

telu_7 <- plot(sm(gam3.3, 68))$ggObj[[1]] %>%
  mutate(bb.sp = rep("telu", n()),
         ktype = rep("head", n()))

wurf_3 <- plot(sm(gam3.3, 69))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("bell", n()))

wurf_5 <- plot(sm(gam3.3, 70))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("lip", n()))

wurf_6 <- plot(sm(gam3.3, 71))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("flag", n()))

wurf_7 <- plot(sm(gam3.3, 72))$ggObj[[1]] %>%
  mutate(bb.sp = rep("wurf", n()),
         ktype = rep("head", n()))

plotting_data <- bind_rows(hort_3, hort_5, hort_6, hort_7,
                           pasc_3, pasc_5, pasc_6, pasc_7,
                           prat_3, prat_5, prat_6, prat_7,
                           soro_3, soro_5, soro_6, soro_7,
                           telu_3, telu_5, telu_6, telu_7,
                           wurf_3, wurf_5, wurf_6, wurf_7) %>%
  group_by(bb.sp, ktype) %>%
  mutate(z.norm = scale(z, center = FALSE),
         ktype = factor(ktype, levels = c("bell", "lip", "flag", "head")),
         date = as_date(x)) %>%
  ungroup() %>%
  left_join(bb_traits) %>%
  left_join(gam3.3_s_table) %>%
  select(z, z.norm, date, x, elevation = y, se, 
         bb.sp, ktype, pbl.w, edf, pval) %>%
  mutate(sig = if_else(pval < 0.05, TRUE, FALSE))

ggplot(plotting_data, aes(date, elevation, z = z.norm, fill = z.norm)) +
  geom_raster() +
  geom_contour(color = "black",
               size = 0.1,
               bins = 40,
               aes(linetype = sig)) + # by fixing bins, we scale contours to each plot while letting the color ramp represent differences in scale across plots; I think this is a good compromise
  facet_grid(reorder(bb.sp, -pbl.w) ~ ktype) +
  scale_linetype_manual(values = c("dotted", "solid"))+
  scale_fill_viridis_c(na.value = "transparent") +
  labs(x = NULL, y = "Elevation (m)", fill = "Normalized\neffect", linetype = "p < 0.05") +
  theme_light(12) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5))
```

### 4.1.2 Model 2 (with prop_abund as covariate)
```{r}
# With abundance covariate (interacting with bb-ktype pair)

## Add abundance data
abundance <- flower_cover_ktype %>%
  separate(sample.id, c("site", "date"), sep = "_") %>%
  group_by(site, date) %>%
  mutate(prop.cover = cover/sum(cover)) %>%
  mutate(ktype = case_when(
    ktype == 0 ~ "null",
    ktype == 1 ~ "disc",
    ktype == 2 ~ "funnel",
    ktype == 3 ~ "bell",
    ktype == 4 ~ "stalk-disc",
    ktype == 5 ~ "lip",
    ktype == 6 ~ "flag",
    ktype == 7 ~ "head",
    ktype == 9 ~ "brush"
  )) %>%
  mutate(ktype = factor(ktype))

null_tab3_join <- null_tab3 %>%
  left_join(abundance) %>%
  mutate(site = factor(site),
         year = factor(year(date)))

## Model with proportional cover data
gam3.2 <- bam(preference ~
                bb.ktype +
                #prop.cover*bb.ktype +
                cover:bb.ktype +
                s(site, by = bb.ktype, bs = "re") +
                s(year, by = bb.ktype, bs = "re") +
                te(yday, elev.mean, by = bb.ktype),
              family = "gaussian",
              method = "fREML",
              discrete = TRUE,
              data = filter(null_tab3_join, 
                            bb.sp %in% c("hort", "prat", "telu", 
                                         "wurf", "soro", "pasc") &
                              ktype %in% c("bell", "lip", "flag", "head"))) %>% 
                getViz()

#check.gamViz(gam3.2)
#gam3.2_corr_sum <- summary(gam3.2, re.test = FALSE)
#print(plot.gamViz(gam3.2, allTerms = TRUE), pages = 4)
```

Since we have a markedly negative effect of abundance on preference, due to the fact that an avoided resource will seem more avoided when it is abundant than when it is rare, even if the cognitive evaluation of the resource does not vary, perhaps it would be worth adding abundance as a covariate to the preference lability model. We do this in model 3.2.

### 4.1.3 Year-specific models
```{r}
# Year-specific models
gam3_2010 <- bam(preference ~
              bb.ktype +
              s(site, by = bb.ktype, bs = "re") +
              te(yday, elev.mean, by = bb.ktype),
            family = "gaussian",
            method = "fREML",
            discrete = TRUE,
            data = filter(null_tab3, 
                          year == 2010 &
                            bb.sp %in% c("hort", "prat", "telu", 
                                       "wurf", "soro", "pasc") &
                            ktype %in% c("3", "5", "6", "7"))) %>% 
              getViz()

@@

# Binomial model
gam5 <- bam(prop.visits ~
              bb.ktype +
              s(site, by = bb.ktype, bs = "re") +
              s(year, by = bb.ktype, bs = "re") +
              te(yday, elev.mean, by = bb.ktype),
            #family = betar(eps = 0.001),
            family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(visit_cover_sitedate, 
                          bb.sp %in% c("pasc", "prat", "telu", "hort", "soro", "wurf") &
                                         ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()

@@

gam6 <- bam(prop.cover ~
              ktype +
              s(site, by = ktype, bs = "re") +
              s(year, by = ktype, bs = "re") +
              te(yday, elev.mean, by = ktype),
            #family = betar(eps = 0.001),
            family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(flower_cover_ktype.prop, 
                            ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()

@@

gam6b <- bam(prop.cover ~
              ktype +
              s(site, by = ktype, bs = "re") +
              s(year, by = ktype, bs = "re") +
              te(yday, elev.mean, by = ktype),
            family = betar(),
            #family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(flower_cover_ktype.prop, 
                            ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()

>>>>

check.gamViz(gam3.1)
gam3.1_sum <- summary(gam3.1, re.test = FALSE)
plot.gamViz(gam3.1, allTerms = TRUE)
```

@@

@@

#### 4.1.1.3 Explore relationship between overall selectivity and the complexity of the elevation-time GAM
```{r}
edf_selectivity <- gam3.1_s_table %>%
  left_join(null_tab1)

ggplot(edf_selectivity, aes(preference, edf)) +
  geom_smooth(method = "lm", color = "black") +
  geom_point(aes(color = bb.sp)) +
  facet_wrap(~ktype) +
  labs(color = "Species", x = "Selectivity", y = "Effective degree of freedom") +
  theme_light(14)

ggsave("../ms_2/figures/edf_selectivity.png")
ggsave("../ms_2/figures/edf_selectivity.pdf")

ggplot(edf_selectivity, aes(preference, edf)) +
  geom_smooth(method = "lm", color = "black") +
  geom_point(aes(color = ktype)) +
  facet_wrap(~bb.sp) +
  labs(color = "Morphotype") +
  theme_light(14)

@@

### 4.3 Year-specific models
```{r}
# Year-specific models
gam3_2010 <- bam(preference ~
              bb.ktype +
              s(site, by = bb.ktype, bs = "re") +
              te(yday, elev.mean, by = bb.ktype),
            family = "gaussian",
            method = "fREML",
            discrete = TRUE,
            data = filter(null_tab3, 
                          year == 2010 &
                            bb.sp %in% c("hort", "prat", "telu", 
                                       "wurf", "soro", "pasc") &
                            ktype %in% c("3", "5", "6", "7"))) %>% 
              getViz()

@@

# Binomial model (works better than beta, probably because of all the ones and zeros)
gam5 <- bam(prop.visits ~
              bb.ktype +
              s(site, by = bb.ktype, bs = "re") +
              s(year, by = bb.ktype, bs = "re") +
              te(yday, elev.mean, by = bb.ktype),
            #family = betar(eps = 0.001),
            family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(visit_cover_sitedate, 
                          bb.sp %in% c("pasc", "prat", "telu", "hort", "soro", "wurf") &
                                         ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()

@@

# Binomial model
gam6 <- bam(prop.cover ~
              ktype +
              s(site, by = ktype, bs = "re") +
              s(year, by = ktype, bs = "re") +
              te(yday, elev.mean, by = ktype),
            #family = betar(eps = 0.001),
            family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(flower_cover_ktype.prop, 
                            ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()

@@

# Beta model (seems to fit a bit better than the binomial model)
gam6b <- bam(prop.cover ~
              ktype +
              s(site, by = ktype, bs = "re") +
              s(year, by = ktype, bs = "re") +
              te(yday, elev.mean, by = ktype),
            family = betar(),
            #family = "binomial",
            method = "fREML",
            discrete = TRUE,
            data = filter(flower_cover_ktype.prop, 
                            ktype %in% c("3", "5", "6", "7"))) %>% 
  getViz()
